### 2014-06-22 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Rename some Figures dirs

\begin{figure}[h!]
\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Pictures/gas_analyzer_5}
\caption{Internal components of the gas analyzer.}
\label{fig:gas_analyzer_5}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Pictures/gas_analyzer_3}
\caption{Internal pump within the gas analyzer.}
\label{fig:gas_analyzer_3}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Figures/gas_analyzer_5}
\caption{Internal components of the gas analyzer.}
\label{fig:gas_analyzer_5}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Figures/gas_analyzer_3}
\caption{Internal pump within the gas analyzer.}
\label{fig:gas_analyzer_3}
\end{figure}
